Scalar Parametrization for Joint Time-Frequency interpolation in a MIMO-OFDM channel

### 2019-10-09 paper/main.tex
Fix images etc.

%% This is a skeleton file demonstrating the use of IEEEtran.cls (requires IEEEtran.cls version 1.8a or later) with an IEEE conference paper.

%%

%% Modified by Khan Reaz( kahn.reaz@ieee.org)

%% Support sites:

%% http://www.ieee.org/

%%***********************************************************

%% Legal Notice:

%% This code is offered as-is without any warranty either expressed or implied; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE!

%% User assumes all risk and can modify as s/he wants.

%%***********************************************************

\def\b0{{\bf 0}}

\def\ba{{\bf a}}

\def\bb{{\bf b}}

\def\bc{{\bf c}}

\def\bd{{\bf d}}

\def\be{{\bf e}}

\def\bg{{\bf g}}

\def\bh{{\bf h}}

\def\bi{{\bf i}}

\def\bj{{\bf j}}

\def\bk{{\bf k}}

\def\bl{{\bf l}}

\def\bm{{\bf m}}

\def\bn{{\bf n}}

\def\bo{{\bf o}}

\def\bp{{\bf p}}

\def\bq{{\bf q}}

\def\br{{\bf r}}

\def\bs{{\bf s}}

\def\bt{{\bf t}}

\def\bu{{\bf u}}

\def\bv{{\bf v}}

\def\bw{{\bf w}}

\def\bx{{\bf x}}

\def\by{{\bf y}}

\def\bz{{\bf z}}

\def\bSigma{{\bf \Sigma}}

\def\bA{{\bf A}}

\def\bB{{\bf B}}

\def\bC{{\bf C}}

\def\bD{{\bf D}}

\def\bE{{\bf E}}

\def\bF{{\bf F}}

\def\bG{{\bf G}}

\def\bH{{\bf H}}

\def\bI{{\bf I}}

\def\bJ{{\bf J}}

\def\bK{{\bf K}}

\def\bL{{\bf L}}

\def\bM{{\bf M}}

\def\bN{{\bf N}}

\def\bO{{\bf O}}

\def\bP{{\bf P}}

\def\bQ{{\bf Q}}

\def\bR{{\bf R}}

\def\bS{{\bf S}}

\def\bT{{\bf T}}

\def\bU{{\bf U}}

\def\bV{{\bf V}}

\def\bW{{\bf W}}

\def\bX{{\bf X}}

\def\bY{{\bf Y}}

\def\bZ{{\bf Z}}

%package list

\documentclass[conference]{IEEEtran}

\IEEEoverridecommandlockouts

\let\labelindent\relax

% \usepackage{breqn}

\usepackage{enumitem}

\usepackage{fleqn}

\usepackage{cite}

\usepackage{graphicx}

\usepackage[varg]{newtxmath}

\graphicspath{ {images/} }

\usepackage{pdfpages}

\usepackage{wrapfig}

\usepackage{fancyhdr}

\usepackage{lastpage}

\usepackage{lettrine}

\usepackage{amsmath}

% \usepackage{titlesec}

\usepackage{mathtools}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\usepackage[colorinlistoftodos]{todonotes}

\usepackage{float}

\usepackage[font={footnotesize}]{caption}

\usepackage[numbers,sort,square,compress]{natbib}

\usepackage[para]{footmisc}

\usepackage{xcolor}

\setlength{\belowcaptionskip}{-12pt}

\newcommand{\highlight}[1]{%

  \colorbox{red!50}{$\displaystyle#1$}}

% \usepackage{parskip}

% \setlength{\parskip}{0.02\baselineskip}

% \fancypagestyle{plain}{

%   \fancyhf{} % sets both header and footer to nothing

% \renewcommand{\headrulewidth}{0pt}

%   \fancyhead[C]{2018 International Conference on Indoor Positioning and Indoor Navigation (IPIN), 24-27 September 2018, Nantes, France}% Right header

% }

\pagestyle{plain}% Set page style to plain.

% \pagestyle{fancyplain}

% \fancyhf{}

% \renewcommand{\headrulewidth}{0pt}

% \fancyhead[C]{2018 International Conference on Indoor Positioning and Indoor Navigation (IPIN), 24-27 September 2018, Nantes, France}

\DeclareMathOperator*{\argmin}{argmin}

% \usepackage{titlesec}

% \titlespacing*{\section}{0pt}{1pt plus 2p}{1ex}

% \titleformat*{\section}{\fontsize{12}{12}\bfseries}

% \titleformat{\section}

%        {\normalfont\fontfamily{phv}\fontsize{12}{17}\bfseries}{\thesection}{1em}{}

% \titleformat{\subsection}

%        {\normalfont\fontfamily{phv}\fontsize{12}{17}\bfseries\itshape}{\thesubsection}{1em}{}

\begin{document}

%Here goes the title

@@

\author{\authorblockN{Author 1, Author 2, Author 3}

\

\authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay}

% \thanks{Parts of this work was supported by the Bharti Centre for Communication in

% Government of India (implemented by the Digital India Corporation).

% }}

}

\maketitle

\thispagestyle{plain}

%Main body starts

% \noindent We consider problem of quantization and interpolation of

% time and frequency varying precoding matrices in wireless MIMO

\begin{abstract}

In a limited feedback MIMO channel, the performance of the channel can improve significantly if the transmitter knows the channel state information (CSI). The receiver knows the channel information, and it feeds back to the transmitter. However, it is not possible to feedback complete information for a limited-feedback OFDM channel since the channel information for multiple subcarriers consumes a large amount of data. Therefore, to resolve this problem, the orthonormality structure of the precoder matrix is exploited to make its one-to-one mapping to a minimal number of scalar parameters. The Precoder matrix is decomposed using Givens Rotation. For an i.i.d. flat-fading Rayleigh channel, these parameters are independent, which makes its quantization and interpolation easy. We propose an efficient method for quantization of the channel state information at the receiver by using adaptive delta modulation for successive time interval. We also propose a method for joint time-frequency interpolation of the channel information at the transmitter.

\end{abstract}

@@

\begin{figure}
\label{adpm-fig}
\includegraphics[width=0.45\textwidth]{images/new-adpm-crop.pdf} 
\caption{Subcarriers which need to be quantized} 
\label{ber_overvie}
\vspace{-5pt} 
\end{figure}

@@

We need to quantize the subcarriers in a way such that we can exploit the joint time-frequency interpolation at the transmitter side. Therefore, we select the subcarriers for quantization in an alternating fashion as shown in the figure. Figure shows a \textbf{N} subcarrier MIMO channel with subcarriers which are going to be quantized at the position sk, k = 0,1,...,$\frac{N-1}{s}$ for even time instance. Here, s is the gap between two frequencies. For odd time instances, subcarriers at the position sk + t for k = 0,1,..., $\frac{N-1}{s}$ with t = $\floor*{\frac{s}{2}}$.

>>>>

\def\b0{{\bf 0}}
\def\ba{{\bf a}}
\def\bb{{\bf b}}
\def\bc{{\bf c}}
\def\bd{{\bf d}}
\def\be{{\bf e}}
\def\bg{{\bf g}}
\def\bh{{\bf h}}
\def\bi{{\bf i}}
\def\bj{{\bf j}}
\def\bk{{\bf k}}
\def\bl{{\bf l}}
\def\bm{{\bf m}}
\def\bn{{\bf n}}
\def\bo{{\bf o}}
\def\bp{{\bf p}}
\def\bq{{\bf q}}
\def\br{{\bf r}}
\def\bs{{\bf s}}
\def\bt{{\bf t}}
\def\bu{{\bf u}}
\def\bv{{\bf v}}
\def\bw{{\bf w}}
\def\bx{{\bf x}}
\def\by{{\bf y}}
\def\bz{{\bf z}}

\def\bSigma{{\bf \Sigma}}
\def\bA{{\bf A}}
\def\bB{{\bf B}}
\def\bC{{\bf C}}
\def\bD{{\bf D}}
\def\bE{{\bf E}}
\def\bF{{\bf F}}
\def\bG{{\bf G}}
\def\bH{{\bf H}}
\def\bI{{\bf I}}
\def\bJ{{\bf J}}
\def\bK{{\bf K}}
\def\bL{{\bf L}}
\def\bM{{\bf M}}
\def\bN{{\bf N}}
\def\bO{{\bf O}}
\def\bP{{\bf P}}
\def\bQ{{\bf Q}}
\def\bR{{\bf R}}
\def\bS{{\bf S}}
\def\bT{{\bf T}}
\def\bU{{\bf U}}
\def\bV{{\bf V}}
\def\bW{{\bf W}}
\def\bX{{\bf X}}
\def\bY{{\bf Y}}
\def\bZ{{\bf Z}}

%package list
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\let\labelindent\relax
% \usepackage{breqn}
\usepackage{enumitem}
\usepackage{fleqn}
\usepackage{cite}
\usepackage{graphicx}
\usepackage[varg]{newtxmath}
\graphicspath{ {images/} }
\usepackage{pdfpages}
\usepackage{wrapfig}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{lettrine}
\usepackage{amsmath}
% \usepackage{titlesec}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage[font={footnotesize}]{caption}
\usepackage[numbers,sort,square,compress]{natbib}
\usepackage[para]{footmisc}
\usepackage{xcolor}
\setlength{\belowcaptionskip}{-12pt}
\newcommand{\highlight}[1]{%
  \colorbox{red!50}{$\displaystyle#1$}}

% \usepackage{parskip}
% \setlength{\parskip}{0.02\baselineskip}

% \fancypagestyle{plain}{
%   \fancyhf{} % sets both header and footer to nothing
% \renewcommand{\headrulewidth}{0pt}
%   \fancyhead[C]{2018 International Conference on Indoor Positioning and Indoor Navigation (IPIN), 24-27 September 2018, Nantes, France}% Right header

% }
\pagestyle{plain}% Set page style to plain.

% \pagestyle{fancyplain}
% \fancyhf{}
% \renewcommand{\headrulewidth}{0pt}
% \fancyhead[C]{2018 International Conference on Indoor Positioning and Indoor Navigation (IPIN), 24-27 September 2018, Nantes, France}
\DeclareMathOperator*{\argmin}{argmin}
% \usepackage{titlesec}

% \titlespacing*{\section}{0pt}{1pt plus 2p}{1ex}
% \titleformat*{\section}{\fontsize{12}{12}\bfseries}
% \titleformat{\section}
%        {\normalfont\fontfamily{phv}\fontsize{12}{17}\bfseries}{\thesection}{1em}{}

% \titleformat{\subsection}
%        {\normalfont\fontfamily{phv}\fontsize{12}{17}\bfseries\itshape}{\thesubsection}{1em}{}

\begin{document}
%Here goes the title

@@

 \author{\authorblockN{Author 1, Author 2, Author 3}
 \
 \authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay}
% \thanks{Parts of this work was supported by the Bharti Centre for Communication in
% IIT Bombay, and the Visvesvaraya
% PhD Scheme of Ministry of Electronics \& Information Technology,
% Government of India (implemented by the Digital India Corporation).
% }}
}
\maketitle

\thispagestyle{plain}
%Main body starts

% \noindent We consider problem of quantization and interpolation of
% time and frequency varying precoding matrices in wireless MIMO
\begin{abstract}
In a limited feedback MIMO channel, the performance of the channel can improve significantly if the transmitter knows the channel state information(CSI). The receiver knows the channel information, and it feeds back to the transmitter. However, it is not possible to feedback complete information for a limited-feedback OFDM channel since the channel information for multiple subcarriers consumes a large amount of data. Therefore to resolve this problem, the orthonormality structure of the precoder matrix is exploited to make its one-to-one mapping to a minimal number of scalar parameters. The Precoder matrix is decomposed using Givens Rotation. For an i.i.d. flat-fading Rayleigh channel, these parameters are independent, which makes its quantization and interpolation easy. We propose an efficient method for quantization of the channel state information at the receiver by using adaptive delta modulation for successive time interval. We also propose a method for joint time-frequency interpolation of the channel information at the transmitter. 153-words
\end{abstract}

@@

\begin{figure}
\label{adpm-fig}
\includegraphics[width=0.45\textwidth]{images/new-adpm.pdf}
\caption{Subcarriers which need to be quantized}
\label{ber_overvie}
\vspace{-5pt}
\end{figure}

@@

We need to quantize the subcarriers in a way such that we can exploit
the joint time-frequency interpolation at the transmitter
side. Therefore, we select the subcarriers for quantization in an
alternating fashion as shown in the figure. Figure shows a \textbf{N}
subcarrier MIMO channel with subcarriers which are going to be
quantized at the position sk, k = 0,1,...,$\frac{N-1}{s}$ for even
time instance. Here, s is the gap between two frequencies. For odd
time instances, subcarriers at the position sk + t for k = 0,1,...,
$\frac{N-1}{s}$ with t = ${\frac{s}{2}}$.
